---
title: "STAT400 Final R proejct Preliminary"
author: "Cheolhong Ahn: UID:114202192 ,  "
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes    
    toc: yes
---


**The dataset Name:**"marketing_capaign.csv"\
**Source:** Kaggle (https://www.kaggle.com/imakash3011/customer-personality-analysis)
```{r}
marketData <- read.csv(file = "marketing_campaign.csv", sep="\t")

```


**summary:**\
Types of variables: Categorical variables, quantitive variables, qualitive varaibles ...\
Variables we plan to use: Education, Income, Year_Birth, Marital_Status, NumWebPurchases, NumStorePurchases\
```{r}
summary(marketData)
```

**Visaul Summaries:**\
Histogram of Ages
```{r}
#Trimmed histogram of Age

#Trim: removes outliers 1.5 times greater than IQR range from mean.
trim <- function(x){
  x[(x > mean(x)-1.5*IQR(x)) & (x < mean(x)+1.5*IQR(x))]
}
hist(trim(marketData$Year_Birth),
     main = "Distribution of age",
     xlab = "Year", 
     ylab = "Number of People", 
     xlim =c(1940,2000),  
     breaks =60 )
  
```

**Possible Ideas:**\
1) Year_Birth vs NumWebPurchases\
   Hypothesis: the ratio of web purchases vs store purchases will increase as\
               the birth year increases\
               
2) Income vs total number of purhcases.\


3) Education vs Marital_Status\





**Task**\

Cheolhong Ahn :\

Suliat Ogunmona :\

Leanne Sto. Domingo :\

Aayush Nepal :\

Yichun Bai :\




